Air cargo load and route planning in pickup and delivery operations

### 2024-01-29 latex/eswa.tex
brazil.png updated

	\end{minipage}\hfill 
	\begin{minipage}{0.42\linewidth}
		\centering
		\includegraphics[scale=0.17]{nodes.png}
		\captionof{figure}{A route with 7 airports}
		\label{fig:nodes}
	\end{minipage}
\end{table}

@@

\textbf{Fleet and Route Planning}: For airline operations, the problem isn't just about finding the shortest path through a set of points but also involves scheduling, aircraft assignment, crew scheduling, and maintenance planning. This multi-dimensional complexity transforms a standard TSP into a more intricate problem in our study, the Pickup and Delivery Problem (PDP).

\textbf{Operational Constraints}: Factors like weather, air traffic control restrictions, and the availability of take-off and landing slots make real-world TSP scenarios in air transport even more challenging. These constraints add layers of complexity that significantly depart from the theoretical TSP model.

@@

In practical air transport scenarios, the size of a TSP can be less about the sheer number of nodes and more about the complexity and dynamic nature of the problem, which in our case (a single aircraft in a single day) is rarely expected to be more than seven nodes. Despite this, at the end of this work, we intend to submit the best method found to a more challenging 15-node problem as a validation test.
}

@@

	\item As the number of nodes is small, we have the possibility to check all possible tours, selecting the one that provides the best value for the objective function. For this reason, a maximum runtime $tmax$\/ per tour is established. In the tests carried out in this work, $tmax \leq 3600s$.

@@

	\item {\color{blue} Lately, the time limit to solve a node will be adjusted to be proportional to the sum of volumes of the candidate items of the node. }

@@

		%% Make the boxes
		\node [mybox] (first)                        { \small {\bf Select:}\\ \small 1. scenario\\ \small 2. surplus\\ \small 3. time limit};
		\node [mybox, right=0.7cm of first] (second) { \small {\bf Config:}\\ \small 4. parameters\\ \small 5. cost matrix\\ \small 6. pallets\\ \small 7. items};
		\node [mybox, right=0.7cm of second] (third) { \small 8. {\bf Define tour}\\  \small      schema:\\ \small - All tours\\ \ \ \ (K-1)!\\ \ \ \  \small or\\ \small - Solve a TSP\\ \small  \ \ \ (set of tours))};
		\node [mybox, right=0.7cm of third] (fourth) { \small {\bf Solve ACLPP+RPDP:}\\ \small 9. Many tours\\ \small  \ \ \ (node-by-node)\\ \small 10. Select best tour};

@@

{\color{blue}
Figure \ref{fig:flow} depicts the Algorithm \ref{alg:main} for easy understanding of the main flow. (1.) Select a scenario from Table \ref{tab:scenarios}. (2.) Select a volume surplus (1.2, 1.5, or 2.0). (3.) Establish a time limit (240s, 1200s, 2400s, or 3600s). (4.) Configure the parameters presented in the mathematical formulation. (5.) Load the distance matrix and calculate the matrix cost according to the aircraft characteristics. (6.) Load the pallet configuration parameters. (7.) Load the item instance (all items to be transported) into memory. (8.) Choose a tour schema. Until 7 nodes, it is practical to generate (K-1)! tours. For a larger number of nodes, we recommend using a TSP heuristic that generates a set of similar suboptimal tours. (9.) and (10.) solve all tours and select the best.
}

>>>>

	\end{minipage}\hfill 
	\begin{minipage}{0.42\linewidth}
		\centering
		\includegraphics[scale=0.21]{nodes.png}
		\captionof{figure}{A route with 7 airports}
		\label{fig:nodes}
	\end{minipage}
\end{table}

@@

\textbf{Fleet and Route Planning}: For airline operations, the problem isn't just about finding the shortest path through a set of points; it also involves scheduling, aircraft assignment, crew scheduling, maintenance planning, and delivering the right cargo to the right client. This last operation task complexity transforms a standard TSP into a more intricate problem in our study, the Pickup and Delivery Problem (PDP).

\textbf{Operational Constraints}: Factors like weather, air traffic control restrictions, and the availability of take-off and landing slots make real-world TSP scenarios in air transport even more challenging. Although we do not deal with these constraints, they add layers of complexity that significantly depart from the theoretical TSP model.

@@

In practical air transport scenarios, the size of a TSP can be less about the sheer number of nodes and more about the complexity and dynamic nature of the problem, which in our case (a single aircraft in a single day) is rarely expected to be more than seven nodes. Despite this, at the end of this work, we to submit the best method found to a more challenging 15-node problem as a validation test.
}

@@

	\item As the number of nodes is small, we have the possibility to check all possible tours, selecting the one that provides the best value for the objective function. For this reason, a maximum runtime $tmax$\/ per tour is established. In the tests carried out in this work, {\color{blue} $tmax \leq [240s, 1200s, 2400s, 3600s]$}.

@@

	\item {\color{blue} Lately, the time limit to solve a node will be adjusted to be proportional to the sum of volumes of the candidate items of the node in relation to the sum of volumes of the entire tour. }

@@

		%% Make the boxes
		\node [mybox] (first)                        { \small {\bf Select:}\\ \small 1. scenario\\ \small 2. surplus\\ \small 3. time limit};
		\node [mybox, right=0.7cm of first] (second) { \small {\bf Config:}\\ \small 4. parameters\\ \small 5. cost matrix\\ \small 6. pallets\\ \small 7. items};
		\node [mybox, right=0.7cm of second] (third) { \small {\bf Define tour}\\  \small {\bf schema:}\\ \small 8. All K! tours\\ \ \ \  \small or\\ \small 8. Solve a TSP\\ \small  \ \ \ (set of tours))};
		\node [mybox, right=0.7cm of third] (fourth) { \small {\bf Solve ACLPP+RPDP:}\\ \small 9. Many tours\\ \small  \ \ \ (node-by-node)\\ \small 10. Select best tour};

@@

{\color{blue}
Figure \ref{fig:flow} depicts the Algorithm \ref{alg:main} for easy understanding of the main flow. (1.) Select a scenario from Table \ref{tab:scenarios}. (2.) Select a volume surplus (1.2, 1.5, or 2.0). (3.) Establish a time limit (240s, 1200s, 2400s, or 3600s). (4.) Configure the parameters presented in the mathematical formulation. (5.) Load the distance matrix and calculate the matrix cost according to the aircraft characteristics. (6.) Load the pallet configuration parameters. (7.) Load the item instance (all items to be transported) into memory. (8.) Choose a tour schema. Until 7 nodes, it is practical to generate K! tours. For a larger number of nodes, we recommend using a TSP heuristic that generates a set of similar suboptimal tours. (9.) and (10.) solve all tours and select the best.
}

### 2024-01-29 latex/responses.tex
Main flow description added
brazil.png updated

		{\color{blue}
		We included the figure below to depict the main algorithm for easy understanding of the main flow.
		}

@@

		%% Make the boxes
\node [mybox] (first)                        {Select:\\ 1. scenario\\2. surplus\\3. time limit};
\node [mybox, right=0.7cm of first] (second) {Config:\\4. parameters\\5. cost matrix\\6. pallets\\7. items};
\node [mybox, right=0.7cm of second] (third) {8. Define tour\\     schema:\\- All tours\\ \ \ \ (K-1)!\\ \ \ \ or\\- Solve a TSP\\ \ \ \ (set of tours))};
\node [mybox, right=0.7cm of third] (fourth) {Solve ACLPP+RPDP:\\9. Many tours\\ \ \ \ (node-by-node)\\10. Select best tour};

>>>>

		{\color{blue}
		We included the figure below and its description to depict the main algorithm for easy understanding of the main flow.
		}

@@

		%% Make the boxes
\node [mybox] (first)                        { \small {\bf Select:}\\ \small 1. scenario\\ \small 2. surplus\\ \small 3. time limit};
\node [mybox, right=0.7cm of first] (second) { \small {\bf Config:}\\ \small 4. parameters\\ \small 5. cost matrix\\ \small 6. pallets\\ \small 7. items};
\node [mybox, right=0.7cm of second] (third) { \small {\bf Define tour}\\  \small {\bf schema:}\\ \small 8. All K! tours\\ \ \ \  \small or\\ \small 8. Solve a TSP\\ \small  \ \ \ (set of tours))};
\node [mybox, right=0.7cm of third] (fourth) { \small {\bf Solve ACLPP+RPDP:}\\ \small 9. Many tours\\ \small  \ \ \ (node-by-node)\\ \small 10. Select best tour};
